Baseline Drift Estimation for Air Quality Data Using Quantile Trend Filtering

### 2019-04-17 Manuscript/detrendify_aoas.tex
more updates

We compare three criteria for choosing the smoothing parameter with our quantile trend filtering method with a single window:  $\V{\lambda}$ chosen using SIC \Eqn{SIC} \citep{KoenkerNgPortnoy1994} (\texttt{detrendr\_SIC}); $\V{\lambda}$ chosen using the validation method with the validation set consisting of every 5th observation (\texttt{detrendr\_valid}); and $\V{\lambda}$ chosen using the proposed scaled eBIC criteria \Eqn{eBIC} \texttt{detrendr\_eBIC}. For the second study we also examine the effect of the non-crossing quantile constraint by estimating the quantile trends separately and choosing $\V{\lambda}$ using the proposed scaled eBIC criteria (\texttt{detrendr\_cross}). We do not include \texttt{detrendr\_cross} in the first study because the difference in quantiles is large enough that we would not expect the non-crossing constraint to make a difference.

>>>>

We compare three criteria for choosing the smoothing parameter with our quantile trend filtering method with a single window:  $\V{\lambda}$ chosen using SIC \Eqn{SIC} \citep{KoenkerNgPortnoy1994} (\texttt{detrendr\_SIC}); $\V{\lambda}$ chosen using the validation method with the validation set consisting of every 5th observation (\texttt{detrendr\_valid}); and $\V{\lambda}$ chosen using the proposed scaled eBIC criteria \Eqn{eBIC} \texttt{detrendr\_eBIC}. For the second study we also examine the effect of the non-crossing quantile constraint by estimating the quantile trends separately and choosing $\V{\lambda}$ using the proposed scaled eBIC criteria (\texttt{detrendr\_Xing}). We do not include \texttt{detrendr\_Xing} in the first study because the difference in quantiles is large enough that we would not expect the non-crossing constraint to make a difference.
